---
title: "Introduction to StatComp22095"
author: "22095"
date: "2022/12/8"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to StatComp22095}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

__StatComp22095__ is a simple R package developed to calculate some indicators of stocks and option prices. There are four functions in total, the first two are __volatility__ and __VAR_and_ES__, which are used to calculate the stock VAR, ES and dynamic volatility. The last two functions __option_price_call_black_scholes__ and __option_price_put_black_scholes__ are compiled with RCPP to calculate the prices of European call options and put options. 

## __volatility__ and __VAR_and_ES__

The source R code for __volatility__ is as follows:
```{r,eval=FALSE}
volatility <- function(data, SMA = TRUE, GMA = TRUE, EWMA = TRUE){
  ##data
  shjc_data <- subset(data,select = c("date","close"))
  
  ##log(1+r)
  shjcnum <- dim(shjc_data)[1]
  SH <- data.frame(date=shjc_data$date[-1],rt= log(shjc_data$close[-1]/shjc_data$close[-shjcnum]))
  
  ##log plot
  par(mfrow = c(1,1))
  plot(SH$rt,type = "l",main = "log(1+r)",col = 3,ylim = c(-0.15,0.15),xlab ="",ylab = "")
  
  
  ## annual dynamic volatility
  #SMA
  N1 <- which(SH$date == "2016-01-04")
  N2 <- which(SH$date == "2021-12-31")
  Num <- N2 - N1 + 1
  SMA_SH <- rep(NA,Num)
  for(i in 1:Num){
    fInd <- N1 + i - 1
    mean_SH <- mean(SH$rt[(fInd - 4):(fInd - 1)])
    SMA_SH[i] <- sqrt(sum((SH$rt[(fInd - 4):(fInd - 1)] - mean_SH)^2/4))
  }
  if (SMA == TRUE){
    print('SMA:')
    print(head(SMA_SH))
  }
  #GMA
  GMA_SH <- rep(NA,Num)
  wt <- c(0.1,0.2,0.3,0.4)
  for(i in 1:Num){
    fInd <- N1 + i - 1
    mean_SH <- mean(SH$rt[(fInd - 4):(fInd - 1)])
    GMA_SH[i] <- sqrt(sum(wt*(SH$rt[(fInd - 4):(fInd - 1)] - mean_SH)^2))
  }
  if (GMA == TRUE){
    print('GMA:')
    print(head(GMA_SH))
  }
  
  #EWMA
  EWMA_SH <- rep(NA,Num);M=4
  lambda <- 0.94;
  vlambda <- c(1,lambda,lambda^2,lambda^3)
  wt <- sort(vlambda/sum(vlambda))
  for(i in 1:Num){
    fInd <- N1 + i - 1
    wtmean_SH <- mean(wt*SH$rt[(fInd-4):(fInd-1)])
    EWMA_SH[i] <- sqrt(sum(wt*(SH$rt[(fInd-4):(fInd-1)]-mean_SH)^2))
  }
  if (EWMA == TRUE){
    print('EWMA:')
    print(EWMA_SH)
  }
  
  ##plot
  Dynavol_SH <- data.frame(date = SH$date[N1:N2], SMA = SMA_SH,GMA = GMA_SH, EWMA = EWMA_SH)
  years <- c("2016","2017","2018","2019","2020","2021") 
  ind_m <- rep(NA,length(years))
  for(i in 1:length(years)){  
    ind_m[i] <- min(which(substr(Dynavol_SH$date,1,4) == years[i])) 
  }
  par(mfrow = c(1,1),pin = c(2,1.2))
  plot(Dynavol_SH$SMA,type = "l",main = "SMA",col = 1,ylim = c(0,0.1),ylab = "",xaxt = "n",xlab ="") 
  axis(side = 1,at = ind_m,labels = years) 
  
  par(mfrow = c(1,1),pin = c(2,1.2))
  plot(Dynavol_SH$GMA,type = "l",main = "GMA",col = 2,ylim = c(0,0.1),ylab = "",xaxt = "n",xlab ="")
  axis(side = 1,at = ind_m,labels = years)
  
  par(mfrow = c(1,1),pin = c(2,1.2))
  plot(Dynavol_SH$EWMA,type = "l",main = "EWMA",col = 3,ylim = c(0,0.1),ylab = "",xaxt = "n",xlab ="")
  axis(side = 1,at = ind_m,labels = years)
  
  print(summary(SH$rt))
}
```


The data is as follows:
```{r,eval=TRUE}
library(StatComp22095)
data(data)
head(data)
tail(data)
```

The specific operation examples are as follows:

```{r,eval=TRUE}
library(StatComp22095)
data(data)
volatility(data, EWMA = TRUE, GMA = FALSE, SMA = FALSE)
```



The source R code for __VAR_and_ES__ is as follows:
```{r,eval=FALSE}
VAR_and_ES <- function(data){
  zuhe_data = subset(data,select = c("date","close"))
  zuhenum = dim(zuhe_data)[1]
  ZUHE=data.frame(date=zuhe_data$date[-1],rt=log(zuhe_data$close[-1]/zuhe_data$close[-zuhenum]))#对数收益率
  
  ##fGarch to compute 1.4(day) VaR
  hT = 800;c = 0.99
  endN = which(ZUHE$date == "2020-12-31")
  staN = endN - hT
  
  
  fit_ZUHE = fGarch::garchFit(~ garch(1,1),data = ZUHE$rt[staN:endN])
  pred_ZUHE = fGarch::predict(fit_ZUHE,n.ahead = 1)##forward one day
  VaR_ZUHE = -(pred_ZUHE$meanForecast + pred_ZUHE$standardDeviation*qnorm(p = 1-c))
  
  ##VaR、ES(year)
  N3 = which(ZUHE$date == "2021-01-04")
  N4 = which(ZUHE$date == "2021-12-31")
  predict_Num = N4 - N3 + 1
  VaR_ZUHE = rep(NA,predict_Num)
  ES_ZUHE = rep(NA,predict_Num)
  for(j in 1:predict_Num){
    pDate = endN + j; pInd = (pDate - hT):(pDate - 1)
    fit_ZUHE = fGarch::garchFit(~ garch(1,1), data = ZUHE$rt[pInd])
    pred_ZUHE = fGarch::predict(fit_ZUHE,n.ahead = 1)
    VaR_ZUHE[j] = -(pred_ZUHE$meanForecast + pred_ZUHE$standardDeviation*qnorm(p = 1-c))
    ES_ZUHE[j]=-(pred_ZUHE$meanForecast+pred_ZUHE$standardDeviation*(-dnorm(qnorm(p = 1-c))/(1-c)))
  }
  
  Risk_ZUHE = data.frame(date = ZUHE$date[N3:N4],VaR = VaR_ZUHE,ES = ES_ZUHE)
  mon = c("2021-01","2021-03","2021-05","2021-07","2021-09","2021-12")
  ind_m1 = rep(NA,length(mon))
  for(i in 1:length(mon)){   
    ind_m1[i] = min(which(substr(Risk_ZUHE$date,1,7) == mon[i])) 
  }
  print(Risk_ZUHE)
  
  par(mfrow = c(1,1),pin = c(2,1.2))
  plot(-Risk_ZUHE$VaR,type = "l",main = "VaR",col = 1,ylim = c(-0.15,0.15),ylab = "",xaxt = "n",xlab = "")
  lines(ZUHE$rt[N3:N4],col = 4)
  axis(side = 1,at = ind_m1,labels = mon)
  
  par(mfrow = c(1,1),pin = c(2,1.2))
  plot(-Risk_ZUHE$ES,type = "l",main = "ES",col = 1,ylim = c(-0.15,0.15),ylab = "",xaxt = "n",xlab = "")
  lines(ZUHE$rt[N3:N4],col = 2)
  axis(side = 1,at = ind_m1,labels = mon)
}
```

The specific operation examples are as follows:

```{r,results='hide',warning = FALSE}
library(StatComp22095)
data(data)
VAR_and_ES(data)
```


## __option_price_call_black_scholes__ and __option_price_put_black_scholes__

The codes of the above two algorithms by Rcpp are as follows:
```{r,eval=FALSE}
double option_price_call_black_scholes(const double& S,
                                       const double& K,
                                       const double& r,
                                       const double& sigma,
                                       const double& time) 
{
  double N(const double& z);
  double time_sqrt = sqrt(time);
  double d1 = (log(S/K)+r*time)/(sigma*time_sqrt)+0.5*sigma*time_sqrt;
  double d2 = d1-sigma*time_sqrt;
  return S*N(d1)-K*exp(-r*time)*N(d2);
}

double N(const double& z) {
  if (z >  6.0) { return 1.0; }; // this guards against overflow
  if (z < -6.0) { return 0.0; };
  double b1 =  0.31938153;
  double b2 = -0.356563782;
  double b3 =  1.781477937;
  double b4 = -1.821255978;
  double b5 =  1.330274429;
  double p  =  0.2316419;
  double c2 =  0.3989423;
  double a=fabs(z);
  double t = 1.0/(1.0+a*p);
  double b = c2*exp((-z)*(z/2.0));
  double n = ((((b5*t+b4)*t+b3)*t+b2)*t+b1)*t;
  n = 1.0-b*n;
  if ( z < 0.0 ) n = 1.0 - n;
  return n;
}

double option_price_put_black_scholes(const double& S,
                                      const double& K,
                                      const double& r,
                                      const double& sigma,
                                      const double& time) // time to maturity
{
  double time_sqrt = sqrt(time);
  double d1 = (log(S/K)+r*time)/(sigma*time_sqrt)+0.5*sigma*time_sqrt;
  double d2 = d1-sigma*time_sqrt;
  return K*exp(-r*time)*N(-d2)-S*N(-d1);
}

option_price_call_black_scholes(4.019, 3.3, 0.022685, 0.4199, 0.05479)
//0.7259894
```
